The Jester joke recommender system

### 2025-03-05 inst/jester.Rmd
consistentify "time to process" information
use new-style suppfun()

@@

```{r,label=calculate_jester,cache=TRUE}
jester <- hyper2()
system.time(for(i in seq_len(nrow(a))){jester <- jester + rank_likelihood(f(a[i,]))})
```

>>>>

<font size="1"> (takes a "long time" to run without cache)
</font>

@@

```{r,label=calculate_jester,cache=TRUE}
jester <- hyper2()
system.time(for(i in seq_len(nrow(a))){jester <- jester + suppfun(f(a[i,]))})
```
